%%% LaTeX Template originaly created by Karol Kozioł (mail@karol-koziol.net) and modified for ShareLaTeX use

\documentclass[a4paper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[british]{babel}
\usepackage[german=quotes]{csquotes}

%\renewcommand\familydefault{\sfdefault}
%\usepackage{tgheros}
%\usepackage[defaultmono]{droidmono}

\usepackage{amsmath,amssymb,amsthm,textcomp}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{tikz}

\usepackage{xcolor}

\usepackage{geometry}
\geometry{left=25mm,right=25mm,%
bindingoffset=0mm, top=20mm,bottom=20mm}
\usepackage{graphicx}
%\usepackage{subcaption}
%\usepackage{mwe}


\linespread{1.3}

\newcommand{\linia}{\rule{\linewidth}{0.5pt}}

% custom theorems if needed
\newtheoremstyle{mytheor}
    {1ex}{1ex}{\normalfont}{0pt}{\scshape}{.}{1ex}
    {{\thmname{#1 }}{\thmnumber{#2}}{\thmnote{ (#3)}}}

\theoremstyle{mytheor}
\newtheorem{defi}{Definition}

% my own titles
\makeatletter
\renewcommand{\maketitle}{
\begin{center}
\vspace{2ex}
{\huge \textsc{\@title}}
\vspace{1ex}
\\
\linia\\
\@author \hfill \@date
\vspace{4ex}
\end{center}
}
\makeatother
%%%

% custom footers and headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
%\lfoot{Assignment \textnumero{} 5}
\cfoot{}
\rfoot{Page \thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
%

% code listing settings
\usepackage{listings}
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    aboveskip={1.0\baselineskip},
    belowskip={1.0\baselineskip},
    columns=fixed,
    extendedchars=true,
    breaklines=true,
    tabsize=4,
    prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
    frame=lines,
    showtabs=false,
    showspaces=false,
    showstringspaces=false,
    keywordstyle=\color[rgb]{0.627,0.126,0.941},
    commentstyle=\color[rgb]{0.133,0.545,0.133},
    stringstyle=\color[rgb]{01,0,0},
    numbers=left,
    numberstyle=\small,
    stepnumber=1,
    numbersep=10pt,
    captionpos=t,
    escapeinside={\%*}{*)}
}

% ref packages
\usepackage{nameref}
% folowing  must be in this order
\usepackage{varioref}
\usepackage{hyperref}
\usepackage{cleveref}

\setlength\parindent{0pt}

%%%----------%%%----------%%%----------%%%----------%%%

\begin{document}

\title{INF273 – Assignment 2}

\author{Lukas Schramm}

\date{\today}

\maketitle

\section{Comments on my code}
I am programming with \texttt{Python} and rewrote the framework we were given but basically followed it's concept. I have written several automatic tests checking if my feasibility-, cost- and reading functions are working and outputing the same results. They all do, but that does not necessarily mean that my code is 100\% code (which makes me nervous). I aim to continue to write automatic tests since I have planned to learn myself testing for ages.

\subsection{Functions}
Currently, I am maintaining the following functions.
\begin{itemize}
\item load\_problem: Given a path to a file, it reads the content of the file into a dictionary of information.
\item feasibility\_check: It takes a solution (list) and a problem dictionary and checks if the solution is feasible. If it is not feasible, it outputs the reason why. It does not check validity (since the aim
\item cost\_function: It takes a solution (list) and a problem dictionary and calculates the cost of the function. As feasibility\_check it does not check if the original solution was valid.
\item splitting\_a\_list\_at\_zeros: Helper function which splits a solution into vehicles and if needed a dummy vehicle.
\item random\_solution: Generates a random solution. The generator itself is quite bad in my view because I overtuned it a bit. It automatically gives one vehicle exactly one call and the rest goes to the dummy vehicle. That way I got solutions for file 3 and 4 but the solutions for all files are quite bad.\footnote{But since we do not need that random solution generator any longer I keep it like that.}
\item blind\_random\_search: Takes a problem and a number of iterations to find the best out of n random feasible solutions if any is found.
\item blind\_search\_latex\_generator: This function runs the blind\_random\_search and writes the data into \LaTeX tables since I am obviously too lazy to do it myself.

If there are any questions or nice recommendations to get a better structure, just send me a message.
\end{itemize}

\clearpage

\section{Result tables}
\input{../Code/solution_table}


\end{document}